Minimax Rates in Contextual Partial Monitoring

### 2018-09-08 pap.tex
working on a different relaxation.

    \inf_{j}  \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ e_j^\top D_i \hat \Delta_t\right]
\mathop{\ex}_{\hat\Delta_t\sim p_t}\left[  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]. 

@@

  \sum_{i=1}^N \min_j \ex_{\hat\Delta_t \sim p_t}

@@

    +\min_j \ex_{\hat\Delta_t'\sim p_t}\left[e_j^\top D_i \hat\Delta_t'\right]

@@

\iffalse
\paragraph{A detail}\todo{remove this paragraph}
While the regret bound, proven w.r.t. the two policies $\pi_1$ and $\pi_2$ and all fixed actions, 
In particular, there exist a policy that is better that $\pi_1$ and $\pi_2$: the one that switches exactly correctly at $\beta$. To fix this, we can instead define
\[
  P_1 = q_1 \mathds{1}\{x \leq \beta-\beta_2\} + q_2 \mathds{1}\{x \geq \beta+\beta_1\}
  + \frac{q_1+q_2}{2}\mathds{1}\{\beta-\beta_2\leq x \leq \beta+\beta_1\}
\]
and analogously for $P_2$. Then the ``perfect policy'' from before does not do any better than $\pi_1$ or $\pi_2$ in expectation.

Unfortunately, this set of alternatives does not have the nice property that the feedback distribution of playing $\pi_1$ under $P_1$ and $P_2$ is identical; there is some small change from $S_1 q_a$ to $S_1 q_b$. It might be possible to balance terms and control the regret.
\fi

>>>>

    \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right].
%   &=
%     \sup_{p_t\in\triangle_{\mathcal D}'}
%     \sum_{i=1}^N
%     \inf_{j}  \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[ e_j^\top D_i \hat \Delta_t\right]
%     +
% \mathop{\ex}_{\hat\Delta_t\sim p_t}\left[  \sup_{\pi\in\Pi} -\pi(x_t)^\top D_i\hat\Delta_t + A_i(\pi)\right]. 

@@

  \min_j \sum_{i=1}^N \ex_{\hat\Delta_t \sim p_t}

@@

      \ex_{\hat\Delta_t'\sim p_t}\left[\pi(x_t)^\top D_i \hat\Delta_t'\right]
     +\sup_{\pi\in\Pi} A_i(\pi)

@@

\section{Structured relaxation}
The partial monitoring problem allows us to write $\Delta_t = V(I_t) S_{I_t} e_{j_t}$ (for some appropriate matrices $V(1),\ldots, V(N)$) and therefore form the unbiased estimate
\[
  \hat\Delta_t = V(I_t) Y_t X_t
\]
where $X_t \sim\text{Bern}\left(\frac{\gamma}{V_\infty} \frac{\Vert V(I_t)^\top Y_t \Vert}{q_t(I_t)}\right)$. The proof for unbiasedness is essentially the same as for the previous relaxation. In particular, $\hat\Delta_t$ can only take on $NM+1$ different values enumerated by the set $U = \{ V(i) S_i e_j: i\in\underbar N, j \in\underbar M\}\cup 0$. Let $u_1,\ldots, u_k$ be an enumeration of this set.
